### 2023-01-02 manuscript.rmd
Address most of the reviewers' comments

---
title             : "Bayesian multilevel modeling and its application in comparative communication research"
shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"

author: 
  - name          : "Chung-hong Chan"
    affiliation   : "1"
    corresponding : yes
    address       : "A5, 6 (section A), 68159 Mannheim, Germany"
    email         : "chung-hong.chan@mzes.uni-mannheim.de"
  - name          : "Adrian Rauschfleisch"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim, Germany"
  - id            : "2"
    institution   : "National Taiwan University, Taiwan"

@@

abstract: |
  Comparative approaches are frequently used in communication research, especially journalism studies. The purpose of this paper is to argue that Bayesian multilevel regression is a better option for analyzing comparative data. We argue that it is the only approach that can simultaneously account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of comparative data. Using the openly available *Worlds of Journalism Study* and *useNews* datasets and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data. We address the common challenges when using the Bayesian approach and highlight the advantages of posterior predictive checks for modeling checking.
keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
wordcount         : "8964"

@@

Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) or their countries (e.g. post-communist country) influence the behaviors of journalists or the content of news articles . For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g., newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g., degree of opinion-orientation), namely, the journalist-level or article-level.

This study of ecological effects on individual behaviors has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found a higher suicide rate among citizens from Scandinavian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research. An example of hypothesis-generating comparative research is <!-- redacted for ijoc  -->AUTHOR1 <!-- @chan2020combining -->, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative study, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions. It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Such data structure brings two problems: non-atomicity and non-stochasticity. And specifically, we propose two solutions: multilevel modeling and Bayesian approach.

The goal of this paper is twofold. We use examples from journalism studies as the most critical cases in communication science to highlight the strength of multilevel models and the advantages of Bayesian models. In our paper, we first discuss these two issues before we suggest Bayesian multilevel regression as the best possible approach for comparative research in communication science and especially in journalism studies. Using the openly available WJS and *useNews* datasets and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.

@@

In comparative research, it is easy to incorrectly assume that macro-level independent variables (e.g. Anglo-American systems) could be analyzed at the same level as the micro-level dependent variable (e.g. the degree of opinion-orientation). The manifestation of this incorrect assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable. Suppose one wants to study how the democratic performance of a country affects journalists’ perceived professional autonomy using the Worlds of Journalism data [Wave 1: @reich:2013:DJP; Wave 2: @hamada:2021:DJA]. The relationship can be expressed in the following regression equation: let $y_{i}$ be the dependent variable at the micro-level (journalist-level: perceived professional autonomy) and $x_{i}$ be the independent variable at the macro-level (country-level: democratic performance). Suppose there are $m$ journalists  where $i = 1,2,\ldots,m$.

@@

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to the so-called atomistic fallacy [@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.). Journalists from the same country are hardly i.i.d.: they are subjected to being governed by the same government and exposed to the same journalistic culture. Also, the way communication researchers survey the journalists resembles (nonrandom) cluster sampling rather than pure random sampling: one usually starts from a specific country and then surveys journalists from it. The choice of  countries is almost always not randomly selected. <!-- [^1] --> This sampling approach makes the independence assumption even more fragile.

<!-- [^1]: If countries were randomly selected, we shall see more African countries in comparative works. It is because 1/4, or 54 out of 195, UN countries are in Africa. -->

Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g. @clarke:2008:W;@chen:2012:IIL]. The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W]. <!-- [^2] -->

<!-- [^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years and it might look repetitious. We believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p. 356] said-- is still not the default regression approach in communication research for hierarchical data and there are many justifications for using the disaggregation approach, e.g. an example in @zhu:2020:S [footnote 5]. <\!-- Even a multilevel modeling textbook advocates these justifications [@bickel2007multilevel]. -\-> See also @nezlek:2008:IMM for a criticism of these justifications.  -->

There are two solutions to this. The first solution is to aggregate the micro-level dependent variable across a macro-level independent variable. Suppose there are $n$ countries in the above example. One can aggregate the average level of $x$ as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$. Then, we can do a regression with a regression equation like so:

@@

Using this aggregation method, the unit of analysis effectively switches from journalist to country. This method is useful when $x$ is the only independent variable. It is not technically committing the atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect. However, this method still has important drawbacks. First, it cannot be used for data with more than two levels. In those cases, the lower-level predictors were lumped together and in effect, assumed to be homogeneous and discarded. Second, this method discards a massive amount of information. It is better for analysis of a dependent micro-level variable with a reasonable aggregation function (e.g. counting a binary variable). For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H]. Also, the effective sample size is reduced from the number of journalists ($m$) to the number of countries ($n$). Third, if one specifies hypotheses at the journalist-level but bases one’s conclusion on the aggregated analysis, this is a risk of interpreting the macro-level association wrongly at the micro-level, otherwise known as ecological fallacy. Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g. $n$) is large. It is also useful to collapse micro-levels (e.g. article-level) that are not useful in answering one’s research questions.

@@

In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average. It is usually set as having a normal distribution with a variance $\tau_{00}$, i.e. $\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$. Instead of a single value, the regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group. It addresses the problem of clustering of articles by macro-level variables. This model is called the varying-intercept model and is used frequently in social science research. We can then study the magnitude of $\gamma_{01}$ to determine the ecological effect.

@@

In sum, multilevel modeling is the way to go for analyzing non-atomic data from comparative research. For surveys using probabilistic sampling, the conventional frequentist approach (maximum likelihood estimation, MLE) might still be valid and is available in most statistical packages [see an SPSS tutorial for communication researchers by @hayes:2006:PMM]. However, @stegmueller:2013:HMC demonstrates that MLE is associated with shrinkage (reduction of standard error, i.e. more false positives) and the shrinkage is more severe when the number of macro-level units (e.g. countries) is small. @stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF]. Although less restrictive methods such as restricted maximum likelihood (REML) have been demonstrated to remediate the shrinkage issue of MLE [@elff:2020:MAF], we still agree with Stegmueller’s proposal for theoretical reasons. And for studies not using probabilistic sampling, we argue in the next section that the Bayesian approach is a better analytical approach.[@western:1994:BIC].

@@

Before diving into our theoretical reasoning, it is important to revisit what frequentist inference, the current default but often misunderstood [@rinke:2018:PMA] mode of inference in communication science, is. Under the frequentist framework, each experiment is assumed to be one of infinite independent, **repeatable** experiments on randomly drawn samples from a population. Random experiments are assumed to be repeated arbitrarily often. Based on this assumption and with just one experiment from the current study, we make an estimation about the population. The discrepancy between the estimation from that one experiment and the actual value of the population is due to sampling error alone, i.e. which subjects were randomly sampled from the population. Randomized surveys, for example, are assumed to be repeatable through repeated random sampling of the population. Suppose we replicated the same survey 100 times and we would obtain a slightly different sample every time. We then calculated the 90\% confidence interval of the mean for each of these 100 surveys. We should anticipate that roughly 90 out of these 100 confidence intervals would include the true mean of the population. We cannot say for sure exactly 90 out of these 100 confidence intervals would include the true mean of the population because repeated random sampling is indeed random and the process is **stochastic**. However, we can say 90 is more probable than 0 or 100.

Most of the comparative content analytic studies, unlike randomized surveys such as WJS, often collect all available content data from a bunch of selected media outlets. In contrast to cluster sampling where media outlets are sampled randomly from a sampling frame of all media outlets, these studies are collecting the entire population of observations from some nonprobailistically selected media outlets. In these census-like situations, there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected **all** available news items from **a selection of major Dutch news outlets**, both online and print" (p. 6, emphasis added) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015. In that study, one could only get more data by including more media outlets or widening the time window. Unlike a repeatable survey like WJS, one can always randomly select more journalists from the sampling frame of all journalists in the respective country.

Therefore, these modern comparative content analytic studies are not repeatable and thus they generate non-stochastic data. It could be argued that data from these comparative content analytic studies are fundamentally irrelevant for frequentist inference [@western:1994:BIC]. Confidence intervals generated do not have the same meaning as those from repeatable studies. According to @western:1994:BIC [p. 413], these values from non-stochastic data "lack meaning even as abstract propositions". [^PVALUES]

[^PVALUES]: In this article, we will not go into detail of the null hypothesis statistical testing (NHST) and p-values, except in the Online Appendix. It is because for studies with a very large N, which comparative studies usually are, NHST is guaranteed to give positive results due to the so-called “Too Big To Fail” problem [see @lin:2013:RCT]. Also, researchers are usually not only interested in whether there is or isn’t an effect. Instead, we are interested in how large the magnitude and in what direction the effect is. Therefore, we will focus only on the point and interval estimations from various regression models.

A common counterargument to this is the classic one from @deming:1941:ICS [p. 45], who suggested that "[a]s a basis for scientific generalizations and decisions for action, a census is only a sample." This notion assumes a census of a population can be used to make inference on a theoretical device called *superpopulation* which "theoretically could exist, may have existed, or may exist in the future" [@gibbs:2015:IU, p.3]. In other words, a finite census-as-a-sample census is assumed to be a “representative sample” of an infinite superpopulation. This counterargument could be useful but unlike a regular random sample (cluster sample included), whose representativeness can be assessed, we can never assess the representativeness of the census-like data with respect to the theoretical superpopulation. Echoing the quote at the beginning of this paragraph, there is no way to tell if the current Czech history is representative of all possible Czech histories in the multiple parallel universes.

Instead of invoking the theoretical device of superpopulation, we follow the arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies: Bayesian inference should be used for analyzing data from comparative research in our field. Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@rinke:2018:PMA]. Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120]. <!-- However, for Bayesian models so-called priors have to be chosen by researchers. -->

Before we move on to the next section, it is important to point out that **non-stochastic data is not an essential condition for applying the Bayesian approach**. The same approach is equally applicable to both non-stochastic and stochastic comparative datasets. Therefore, one can analyze both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach. Besides these more abstract conceptual implications, choosing a Bayesian approach has some practical advantages, as we will later illustrate with the posterior predictive checks (PPCs), which can only be calculated if a Bayesian approach is used.

@@

What is the probability for this paper being accepted by *IJOC*? Under the frequentist framework (and if *IJOC* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *IJOC*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *IJOC*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate of a similar journal. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is mixed reviewed by three reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).

Without repeated experiment, these probabilities quantify our certainty on how likely this paper is being accepted, given the current available data . We revise our old beliefs (or **prior**, $p(\theta)$) with the new data ($X$) and form our revised belief (or **posterior**, $p(\theta|X)$). This can be summarized in the following equation [@gelman2020bayesian]:

@@

Undoubtedly, setting prior is consequential to the analysis. But the influence from priors is greatly weakened, when the data is getting bigger. Other than expert elicitation, another non-controversial way to specify priors --- at least in our opinion --- is to use a weakly informative prior [@lemoine:2019:M]. In this way, one specifies only the possible range of the posterior<!-- [^4] -->. Some so-called "default weakly informative priors", e.g. $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008].

<!-- [^4]: One could also use a completely *noninformative* prior such as $\mathcal{U}(-\infty, \infty)$. It is, however, no longer advised. -->

@@

<!-- *"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modeling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p. 19] -->

Bayesian analysis is still a minority statistical method in social sciences. It is reasonable to say that Bayesian analysis is extremely rare in our field. Although some communication researchers adopted the method (e.g. AUTHOR2, AUTHOR3) <!-- [e.g. @kovic:2017:B;@chan2020high] -->, these studies are not comparative. As far as we know, the only available comparative communication research that Bayesian multilevel regression was used for studying ecological effect are @leeuw:2020:AAT and @heidenreich:2022:DE. We believe comparative communication research fits the use case of Bayesian multilevel regression analysis.This paper demonstrates how to do the analysis using the R package *brms* [@burkner2017advanced] (see the source code in the Online Appendix https://osf.io/2h4w8/?view_only=be14dc637b8e4fd1a26ac5c64682b6d9 ). As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar. <!-- The above-quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.  -->

@@

In this example, the Bayesian approach is applied to a stochastic dataset from a randomized survey. The starting point of this example is the recent study by @hamada:2021:DJA. Using the second wave data from WJS (2012-2016), the study seeks to study this hypothesis (the H2a in the paper): *The greater the level of democracy in a country, the more perceived professional autonomy journalists enjoy*. To rephrase this, the level of democracy in a country has an ecological effect on the journalists’ perceived professional autonomy.

It is important to point out that the study is a replication. The same hypothesis has been studied in the earlier study by @reich:2013:DJP, which uses the first wave data from WJS and has a remarkably similar title to that of @hamada:2021:DJA. The earlier study has studied this hypothesis (the H4): *Journalists’ perceived professional autonomy is positively associated with democratic performance and press freedom, and it is negatively related to political parallelism and state intervention.* The operationalizations of both professional autonomy (based on two questions in WJS) and level of democracy (based on the Economist Intelligence Unit's Index of Democracy) are the same in the two studies. It is important to recite the operationalization of professional autonomy here. The two questions in the survey are: (1) “Thinking of your work overall, how much freedom do you personally have in selecting news stories you work on?” (2) “How much freedom do you personally have in deciding which aspects of a story should be emphasized?” The possible answers ranged from 5 = “complete freedom” to 1 = “no freedom at all”. The two answers were averaged. We will come back to this operationalization later in this article.

@@

Let's assume we were in the shoes of @hamada:2021:DJA and wanted to replicate the study by @reich:2013:DJP with the second wave WJS data. Bayesian multilevel regression is a better approach.

>>>>

---
title             : "Bayesian multilevel modeling and its application in comparative journalism studies"
shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"

author: 
  - name          : "Chung-hong Chan"
    affiliation   : "1"
    corresponding : yes
    address       : "Unter Sachsenhausen 6-8, 50667 Köln"
    email         : "chung-hong.chan@gesis.org"
  - name          : "Adrian Rauschfleisch"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "GESIS – Leibniz-Institut für Sozialwissenschaften, Germany"
  - id            : "2"
    institution   : "National Taiwan University, Taiwan"

@@

abstract: |
  Comparative approaches are frequently used in communication research, especially journalism studies. The purpose of this paper is to argue that Bayesian multilevel regression is the most justifiable option for analyzing comparative data. We argue that it is the only approach that can simultaneously account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of comparative data. Using the openly available *Worlds of Journalism Study* and *useNews* datasets, we demonstrate how to apply the Bayesian approach for the analysis of comparative data. We address the common challenges when using the Bayesian approach and highlight the advantages of posterior predictive checks for modeling checking.
keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
wordcount         : "8964"

@@

Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) or their countries (e.g. post-communist country) influence the behaviors of journalists or the content of news articles. For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g., newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g., degree of opinion-orientation), namely, the journalist-level or article-level.

This study of ecological effects on individual behaviors has a long tradition in communication research. There are hypothesis-generating and hypothesis- testing comparative studies. An example of hypothesis-generating comparative research is <!-- redacted for ijoc  -->AUTHOR1 <!-- @chan2020combining -->, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative study, however, is rare. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying independence of observations assumption of linear regression (See non-atomicity below). It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Such data structure brings two problems: non-atomicity and non-stochasticity. And specifically, we propose two solutions: multilevel modeling and Bayesian approach.

The goal of this paper is twofold. We use examples from journalism studies as the most critical cases in communication science to highlight the strength of multilevel models and the advantages of Bayesian models. In our paper, we first discuss these two issues and then suggest Bayesian multilevel regression as the most defensible option. Using the openly available WJS and *useNews* datasets, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.

@@

In comparative research, it is easy to assume that macro-level independent variables (e.g. Anglo-American systems) could be analyzed at the same level as the micro-level dependent variable (e.g. the degree of opinion-orientation). The manifestation of this assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable. Suppose one wants to study how the democratic performance of a country affects journalists’ perceived professional autonomy using the WJS data [Wave 1: @reich:2013:DJP; Wave 2: @hamada:2021:DJA]. The relationship can be expressed in the following regression equation: let $y_{i}$ be the dependent variable at the micro-level (journalist-level: perceived professional autonomy) and $x_{i}$ be the independent variable at the macro-level (country-level: democratic performance). Suppose there are $m$ journalists  where $i = 1,2,\ldots,m$.

@@

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to the so-called atomistic fallacy [@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.). Journalists from the same country are hardly i.i.d.: they are subjected to being governed by the same government and exposed to the same journalistic culture. Also, the way communication researchers survey the journalists resembles (nonrandom) cluster sampling rather than pure random sampling: one usually starts from a specific country and then surveys journalists from it. The choice of countries is almost always not randomly selected. This sampling approach makes the independence assumption even more fragile. Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g. @clarke:2008:W;@chen:2012:IIL].

There are two solutions to this [^indieerror]. The first solution is to aggregate the micro-level dependent variable across a macro-level independent variable. Suppose there are $n$ countries in the above example. One can aggregate the average level of $x$ as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$. Then, we can do a regression with a regression equation like so:

[^indieerror]: In general, the non-atomicity alone only influences the inference (e.g. p-values, confidence intervals) by increasing the chance of Type I errors. The magnitude of the regression coefficient should still be consistent. Another approach, which we are not going to discuss in detail, is to use the clustered-robust standard error. For a survey of the technique, see @wooldridge:2003:CSM. The technique can only address the non-atomicity issue alone, but not non-stochasticity.

@@

Using this aggregation method, the unit of analysis effectively switches from journalist to country. This method is useful when $x$ is the only independent variable. It is not technically committing the atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect. However, this method still has important drawbacks. First, it cannot be used for data with more than two levels. In those cases, the lower-level predictors were lumped together and in effect, assumed to be homogeneous and discarded. Second, this method discards a massive amount of information. It is useful only for analysis of a dependent micro-level variable with a reasonable aggregation function (e.g. counting a binary variable). For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H]. Also, the effective sample size is reduced from the number of journalists ($m$) to the number of countries ($n$). Third, if one specifies hypotheses at the journalist-level but bases one’s conclusion on the aggregated analysis, this is a risk of interpreting the macro-level association wrongly at the micro-level, otherwise known as ecological fallacy. Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g. $n$) is large. It is also useful to collapse micro-levels (e.g. article-level) that are not useful in answering one’s research questions.

@@

In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average [^pooling]. It is usually set as having a normal distribution with a variance $\tau_{00}$, i.e. $\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$. Instead of a single value, the regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group. It addresses the problem of clustering of articles by macro-level variables. This model is called the varying-intercept model and is used frequently in social science research. We can then study the magnitude of $\gamma_{01}$ to determine the ecological effect.

[^pooling]: One can also think about this in terms of pooling: how the data from different groups are combined. We can have complete pooling (the disaggregation approach, just one slope), no pooling (each group should be modelled individually and each group has a different slope), and partial pooling (each group does have a unique slope. But the distribution of all slopes follow a distribution).

@@

In sum, multilevel modeling is more justifiable for analyzing non-atomic data from comparative research. For surveys using probabilistic sampling, the conventional frequentist approach (maximum likelihood estimation, MLE) might still be valid and is available in most statistical packages [see an SPSS tutorial for communication researchers by @hayes:2006:PMM].

@@

@stegmueller:2013:HMC demonstrates that MLE for multilevel modeling is associated with shrinkage (reduction of standard error, i.e. more false positives) and the shrinkage is more severe when the number of macro-level units (e.g. countries) is small. @stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF]. Although less restrictive methods such as restricted maximum likelihood (REML) have been demonstrated to remediate the shrinkage issue of MLE [@elff:2020:MAF], we still agree with Stegmueller’s proposal for theoretical reasons [@western:1994:BIC].

Before diving into our theoretical reasoning, it is important to revisit what frequentist inference is. Under the frequentist framework, each experiment is assumed to be one of infinite independent, **repeatable** experiments on randomly drawn samples from a population. Random experiments are assumed to be repeated arbitrarily often. Based on this assumption and with just one experiment from the current study, we make an estimation about the population. The discrepancy between the estimation from that one experiment and the actual value of the population is due to sampling error alone, i.e. which subjects were randomly sampled from the population. Randomized surveys, for example, are assumed to be repeatable through repeated random sampling of the population. Suppose we replicated the same survey 100 times and we would obtain a slightly different sample every time. We then calculated the 90\% confidence interval of the mean for each of these 100 surveys. We should anticipate that roughly 90 out of these 100 confidence intervals would include the true mean of the population. We cannot say for sure exactly 90 out of these 100 confidence intervals would include the true mean of the population because repeated random sampling is indeed random and the process is **stochastic**. However, we can say 90 is more probable than 0 or 100.

Most of the comparative content analytic studies, for example, often collect all available content data from a bunch of selected media outlets. In contrast to cluster sampling where media outlets are sampled randomly from a sampling frame of all media outlets, these studies are collecting the entire population of observations from some nonprobailistically selected media outlets. In these census-like situations, there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected **all** available news items from **a selection of major Dutch news outlets**, both online and print" (p. 6, emphasis added) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015. In that study, one could only get more data by including more media outlets or widening the time window [^conventionalcontentanalysis]. Unlike a (theoretically) repeatable survey like WJS, one can randomly select more journalists from the sampling frame of all journalists in the respective country.

[^conventionalcontentanalysis]: Comparative content analytic studies can also be performed without this census-like approach. The traditional approach of making probabilistic sample from all units can also be used [@krippendorff2018content]. As there is an explicit sampling frame of all units, the population of content about which the sample is making inference from is known in this case. Any further inference made beyond the population is speculative.

Therefore, these modern comparative content analytic studies are often not repeatable and thus they generate non-stochastic data. It could be argued that data from these comparative content analytic studies with a census-like approach are fundamentally irrelevant for frequentist inference [@western:1994:BIC]. Confidence intervals generated do not have the same meaning as those from repeatable studies. According to @western:1994:BIC [p. 413], these values from non-stochastic data "lack meaning even as abstract propositions". [^PVALUES]

[^PVALUES]: In this article, we will not go into detail of the null hypothesis statistical testing (NHST) and p-values, except in the Online Appendix. Researchers are usually not only interested in whether there is or isn’t an effect. Instead, we are interested in how large the magnitude and in what direction the effect is. Therefore, we will focus only on the point and interval estimations from various regression models.

A common counterargument to this is the classic one from @deming:1941:ICS [p. 45], who suggested that "[a]s a basis for scientific generalizations and decisions for action, a census is only a sample." This notion assumes a census of a population can be used to make inference on a theoretical device called *superpopulation* which "theoretically could exist, may have existed, or may exist in the future" [@gibbs:2015:IU, p.3]. In other words, a finite census-as-a-sample census is assumed to be a "representative sample" of an infinite superpopulation. This counterargument could be useful but unlike a regular random sample (cluster sample included), whose representativeness can be assessed, we can never assess the representativeness of the census-like data with respect to the theoretical superpopulation. Echoing the quote at the beginning of this paragraph, there is no way to tell if the current Czech history is representative of all possible Czech histories in the multiple parallel universes.

Instead of invoking the theoretical device of superpopulation, we follow the arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies: Bayesian inference should be used for analyzing data from comparative research in our field. Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@rinke:2018:PMA]. Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].

Before we move on to the next section, it is important to point out that **non-stochastic data is not an essential condition for applying the Bayesian approach**. The same approach is equally applicable to both non-stochastic and stochastic comparative datasets.

@@

What is the probability for this paper being accepted by *IJOC*? Under the frequentist framework (and if *IJOC* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *IJOC*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *IJOC*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate of a similar journal. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is mixed reviewed by three reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100%. If we (or other researchers) "repeat the experiment" and resubmit the same paper again to *IJOC*, the probability of the resubmitted paper for being accepted is 0%.

Without repeated experiment, these probabilities quantify our certainty on how likely the paper is being accepted, given the current available data . We revise our old beliefs (or **prior**, $p(\theta)$) with the new data ($X$) and form our revised belief (or **posterior**, $p(\theta|X)$). This can be summarized in the following equation [@gelman2020bayesian]:

@@

Undoubtedly, setting prior is consequential to the analysis. But the influence from priors is greatly weakened, when the data is getting bigger. Other than expert elicitation, another non-controversial way to specify priors --- at least in our opinion --- is to use a weakly informative prior [@lemoine:2019:M]. In this way, one specifies only the possible range of the posterior. Some so-called "default weakly informative priors", e.g. $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008].

@@

Bayesian analysis is still a minority statistical method in social sciences. As far as we know, the only available comparative communication research that Bayesian multilevel regression was used for studying ecological effect are @leeuw:2020:AAT and @heidenreich:2022:DE. As argued in the two previous sections,
comparative communication research fits the use case of Bayesian multilevel regression analysis. This paper demonstrates how to do the analysis using the R package *brms* [@burkner2017advanced] (see the source code in the Online Appendix https://osf.io/2h4w8/?view_only=be14dc637b8e4fd1a26ac5c64682b6d9 ). As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar.

@@

In this example, the Bayesian approach is applied to a stochastic dataset from a survey in which some randomization is involved. The starting point of this example is the recent study by @hamada:2021:DJA. Using the second wave data from WJS (2012-2016), the study seeks to study this hypothesis (the H2a in the paper): *The greater the level of democracy in a country, the more perceived professional autonomy journalists enjoy*. To rephrase this, the level of democracy in a country has an ecological effect on the journalists’ perceived professional autonomy.

It is important to point out that the study is a replication. The same hypothesis has been studied in the earlier study by @reich:2013:DJP, which uses the first wave data from WJS and has a remarkably similar title to that of @hamada:2021:DJA. The earlier study has studied this hypothesis (the H4): *Journalists’ perceived professional autonomy is positively associated with democratic performance and press freedom, and it is negatively related to political parallelism and state intervention.* The operationalizations of both professional autonomy (based on two questions in WJS) and level of democracy (based on the Economist Intelligence Unit's Index of Democracy) are the same in the two studies. It is important to recite the operationalization of professional autonomy here. The two questions in the survey are: (1) "Thinking of your work overall, how much freedom do you personally have in selecting news stories you work on?" (2) "How much freedom do you personally have in deciding which aspects of a story should be emphasized?" The possible answers ranged from 5 = "complete freedom" to 1 = "no freedom at all". The two answers were averaged.

@@

Let's assume we were in the shoes of @hamada:2021:DJA and wanted to replicate the study by @reich:2013:DJP with the second wave WJS data. Bayesian multilevel regression provides several advantages over the aggregated approach.
